Model Search in Relational Domains

### 2016-10-23 deductions.tex
section 5 check

The {\em forward} propagation strategy initialises the worklist with
abstract deduction transformers that contain constants in the
right-hand side and the subdomain is constructed via $\makesubdomain$
from variables in left-hand side of the equality constraints
originating from the assignment statements in the program.
%
The {\em backward} propagation strategy initialises the worklist 
with the assertions and the subdomain is constructed from the 
right-hand side variables.
%
The {\em multi-way} propagation strategy initialises the worklist 
with the set of all transformers and the corresponding subdomains 
contains the variables occurring in the respective transformers.
%
Depending on the propagation heuristics, $\updateworklist$ adds
abstract deduction transformers to the worklist that contain variables
that appear in $\newdeductions$, and updates the subdomains of
the abstract deduction transformers in the worklist 
to include the variables in $\newdeductions$.
%
The function
$\onlynew(\absval)=\bigsqcap(\decomp(\absval)\setminus\decomp(\abs(\trail)))$
is used to filter out all meet irreducibles that are already on the trail
in order to obtain only new deductions when applying the abstract deduction transformer.
%
\Omit{
If $\bot$ is deduced we return \textsf{conflict}.
Otherwise, when eventually a fixed point has been reached, i.e.\ the worklist is empty, then the abstract value $\abs(\trail)$ is checked whether it is 
$\gamma$-complete~\cite{dhk2013-popl}. 
%
It is $\gamma$-complete if all concrete values in $\gamma(\abs(\trail))$ satisfy $\formula$.
Otherwise, the algorithm returns \textsf{unknown} and ACDCL makes a new decision.}

If $\abstransel{\subdomain}$ deduces $\bot$, then 
the procedure $\mathit{deduce}$ returns \textsf{conflict}.
Otherwise, when a fixed-point is reached, i.e.\ 
the worklist is empty, then we check whether
the abstract transformers $\abstransset$ are $\gamma$-complete~\cite{dhk2013-popl} for the current abstract value $\abs(\trail)$.
%
Intuitively, this means that all concrete values in 
$\gamma(\absval)$ satisfy $\formula$.  
%
If it is indeed 
$\gamma$-complete, then $\mathit{deduce}$ returns \textsf{sat}.  Otherwise, the 
algorithm returns \textsf{unknown} and ACDCL makes a new decision.

>>>>

The {\em forward} propagation strategy initialises the worklist with
abstract deduction transformers that contain constants in the
right-hand side and the subdomain is constructed via $\makesubdomain_\domain$
from variables in the left-hand side of the equality constraints
originating from the assignment statements in the program.
%
The {\em backward} propagation strategy initialises the worklist 
with the assertions and the subdomain is constructed from the 
right-hand side variables.
%
The {\em multi-way} propagation strategy initialises the worklist 
with the set of all transformers and the corresponding subdomains 
contains the variables occurring in the respective transformers.
%
Depending on the propagation heuristics, $\updateworklist$ adds
abstract deduction transformers to the worklist that contain variables
that appear in $\newdeductions$, and updates the subdomains of
the abstract deduction transformers in the worklist 
to include the variables in $\newdeductions$.
%
The function
$\onlynew(\absval)=\bigsqcap(\decomp(\absval)\setminus\decomp(\abs(\trail)))$
is used to filter out all meet irreducibles that are already on the trail
in order to obtain only new deductions when applying the abstract deduction transformer.
%
\Omit{
If $\bot$ is deduced we return \textsf{conflict}.
Otherwise, when eventually a fixed point has been reached, i.e.\ the worklist is empty, then the abstract value $\abs(\trail)$ is checked whether it is 
$\gamma$-complete~\cite{dhk2013-popl}. 
%
It is $\gamma$-complete if all concrete values in $\gamma(\abs(\trail))$ satisfy $\formula$.
Otherwise, the algorithm returns \textsf{unknown} and ACDCL makes a new decision.}

If $\abstransel{\subdomain}$ deduces $\bot$, then 
the procedure $\mathit{deduce}$ returns \textsf{conflict}.
Otherwise, when a fixed-point is reached, i.e.\ 
the worklist is empty, then we check whether
the abstract transformers $\abstransset$ are $\gamma$-complete~\cite{dhk2013-popl} for the current abstract value $\abs(\trail)$.
%
Intuitively, this means that all concrete values in 
$\gamma(\abs(\trail))$ satisfy $\formula$.  
%
If it is indeed 
$\gamma$-complete, then $\mathit{deduce}$ returns \textsf{sat}.  Otherwise, the 
algorithm returns \textsf{unknown} and ACDCL makes a new decision.
